\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=1in}

\title{Food Waste Reduction Platform\\Performance and Quality Assurance}
\date{}

\begin{document}

\maketitle

% ====================== SECTION 6: PERFORMANCE AND QUALITY ASSURANCE ======================
\section{Performance and Quality Assurance}

To ensure that the Food Waste Reduction Platform operates efficiently, reliably and at scale, the system incorporates a structured performance monitoring framework based on measurable Key Performance Indicators (KPIs), continuous monitoring strategies, and a feedback-driven improvement cycle.

\subsection{Key Performance Indicators}

The following KPIs are used to evaluate system effectiveness, operational
performance and social impact (see Table~\ref{tab:kpis} in Appendix~\ref{app:kpis}).

\subsection{Monitoring Strategy}

The platform includes an operational monitoring layer designed to continuously track system performance and detect anomalies in real time.

The monitoring strategy includes the following mechanisms:

\begin{itemize}
    \item \textbf{Operational Logging}: All system events (surplus publication, matching operations, notifications, and pickups) are recorded in centralized logs.
    
    \item \textbf{Real-Time Metrics Collection}: Key system metrics such as response time, concurrent users, and assignment success rate are collected continuously by the analytics module.
    
    \item \textbf{Administrative Dashboard}: The Admin Dashboard provides real-time visualization of operational indicators such as recovered kilograms, success rate, supplier activity trends, and pickup completion rates.
    
    \item \textbf{Automated Alerts}: Alerts are triggered when predefined thresholds are exceeded, such as high no-show rates, increasing response times, or decreasing surplus recovery rates.
\end{itemize}

These monitoring mechanisms allow administrators to identify performance issues quickly and respond before they significantly impact the system.

\subsection{Success Criteria and Continuous Improvement Plan}

System success is evaluated based on measurable operational outcomes and long-term participation sustainability.

The platform is considered to be operating successfully when the following criteria are consistently met:

\begin{itemize}
    \item At least \textbf{80\% of published surplus food is successfully redistributed}.
    \item The \textbf{matching algorithm generates assignments within 2 seconds}.
    \item The \textbf{pickup completion rate remains above 85\%}.
    \item Push notifications are delivered in \textbf{less than 5 seconds for at least 95\% of users}.
\end{itemize}

To ensure long-term improvement, the platform follows a continuous improvement cycle:

\begin{itemize}
    \item \textbf{Weekly metric reviews} performed by system administrators to detect operational trends.
    \item \textbf{Algorithm tuning} based on observed matching fairness, pickup reliability, and geographic distribution.
    \item \textbf{User behavior analysis} to detect repeated no-shows or anomalous claiming patterns.
    \item \textbf{System performance optimization} based on observed load patterns during peak hours.
\end{itemize}

This iterative monitoring and improvement approach ensures that the platform remains scalable, fair, and effective in reducing food waste while maintaining high operational reliability.

\appendix

\section{Key Performance Indicators}
\label{app:kpis}

Table~\ref{tab:kpis} shows the KPIs used to evaluate system effectiveness.

\begin{table*}[!t]
\centering
\caption{Key Performance Indicators}
\label{tab:kpis}

\begin{tabular}{p{3.5cm} p{9cm} p{3cm}}
\toprule
\textbf{KPI} & \textbf{Description} & \textbf{Target Value} \\
\midrule

Surplus Recovery Rate & Percentage of published food surplus that is successfully collected. & $\geq$80\% \\

Average Matching Time & Time required by the matching engine to assign a collector after publication. & $<$2 seconds \\

Successful Pickup Rate & Percentage of confirmed assignments that result in completed pickups. & $\geq$85\% \\

Notification Delivery Time & Time required to deliver push notifications to candidate users. & $<$5 seconds \\

System Response Time & Average backend API response time during normal operation. & $<$500 ms \\

Concurrent User Capacity & Maximum number of simultaneous active users supported without performance degradation. & $\geq$200 users \\

\bottomrule
\end{tabular}

\end{table*}

\end{document}